Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-06-22 ltx/PLoS/LaTeX_Manuscript.tex
editing algorithm table

	\label{DefFieldDecomp} v_t\left(\mathbf{r}\right) \approx \boldsymbol{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t, 

@@

\begin{table}[!ht]
\caption{
\bf{The Unscented RTS Smoother}}
\begin{tabular}{|c|}
\multicolumn{1}{|p{16cm}|}{ 1. Forward initialisation} \\
$\hat{\mathbf x}_0, \mathbf P_0$ \\
\multicolumn{1}{|p{16cm}|}{   Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
	$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
\multicolumn{1}{|p{16cm}|}{   Calculate the predicted state and the predicted covariance matrix} \\
$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1}$
\end{tabular}
\begin{flushleft}Table caption
\end{flushleft}
\label{tab:label}
\end{table}

>>>>

	\label{DefFieldDecomp} v_t\left(\mathbf{r}\right) \approx \mathbf{\phi}^{\top}\left(\mathbf{r}\right) \mathbf{x}_t, 

@@

\begin{table}[!ht]
\caption{
\bf{The Unscented RTS Smoother}}
\begin{tabular}{|c|}\hline
\multicolumn{1}{|p{16cm}|}{ 1. Forward initialisation} \\ 
\\
$\hat{\mathbf x}_0, \mathbf P_0$ \\
\\
\multicolumn{1}{|p{16cm}|}{   Forward iteration: for $t \in \left\lbrace 0,\cdots, T\right\rbrace $, calculate the sigma points $\mathcal X_{i,t}^f$ using equations \ref{eq:sigmapoints1}-\ref{eq:sigmapoints3} and propagate through equation~\ref{eq:QmatrixForSigmapoints}} \\
\\
	$\mathcal X_{i,t+1}^{f-}=Q(\mathcal X_{i,t}^f) \quad i=0, \dots, 2L$\\
	\\
\multicolumn{1}{|p{16cm}|}{   Calculate the predicted state and the predicted covariance matrix} \\
\\
$\hat{\mathbf x}_{t+1}^{f-}=\sum_{i=0}^{2L} W_i^{(m)}\mathcal X_{i,t+1}^{f-} $ \\
\\
$\mathbf P_{t +1}^{f-}=\sum_{i=0}^{2L} W_i^{(c)}(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})(\mathcal X_{i,t+1}^{f-}-\hat{\mathbf x}_{t +1}^{f-})^\top+\boldsymbol \Sigma_e$ \\ 
\\
\multicolumn{1}{|p{16cm}|}{Compute the filter gain, the filtered state and the filtered covariance matrix using the standard Kalman filter update equations} \\
\\
$\mathcal K_{t+1}=\mathbf P_{t +1}^{f-}\mathbf C ^\top(\mathbf C \mathbf P_{t +1}^{f-}\mathbf C ^\top+\boldsymbol \Sigma_{\epsilon})^{-1}$\\
\\
$\hat{\mathbf x}_{t+1}^{f}=\hat{\mathbf x}_{t+1}^{f-}+\mathcal K_{t+1}(\mathbf y_{t+1}-\mathbf C\hat{\mathbf x}_{t +1}^{f-}) $\\
\\
$\mathbf P_{t+1}^f=(\mathbf I - \mathcal K_{t+1}\mathbf C)\mathbf P_{t +1}^{f-}$\\ 
\\\hline
\multicolumn{1}{|p{16cm}|}{2. Backward initialisation}\\
\\
$\mathbf P_T^b= \mathbf P_T^f, \quad \hat{\mathbf x}^b_T= \hat{\mathbf x}^f_T$ \\
\\

\end{tabular}
\begin{flushleft}Table caption
\end{flushleft}
\label{tab:label}
\end{table}
